Topic 6.2: Open Data

### 2020-05-07 draft_chapter.Rmd
Discussion

Open data are a response to these shortcomings, broadening access and participation in research, removing the requirement for permissions, formal agreements and negotiations [@manovich2011trending]. Not only this, but open data can also lead to all sorts of novel insight within criminology and cime and place research, tapping into constructs and processes which are difficult to capture through surveys, interviews and other traditional meaures [@solymosi2018role]. As such, it is important that social scientists, researchers, crime analysts, and others interested in making sense of the social world around them have the skills and know-how to access, accurately interpret, assess and analyse open data sets.

@@

In short, 'open data' should be data that are readily and publicly available, in a usable format, and without reistrictions on usage, modification and re-distribution.

@@

As researchers studying crime and place, public sector data is particularly important. Many variables thought to explain the non-random distribution of crime, offenders and victims in space are coallated and published by governmental bodies. For instance, demographic characteristics about resident populations can be collected via national censuses, with data usually released at aggregations which constitute 'neighbourhoods' - a theoretically important scale in criminology. Data describing urban structure, such as street networks, are often generated and distributed by public bodies, and can be used in street syntax analysis to assess whether the configeration of streets dictates things like violent crime victimisation [@streetsyntax2017]. In many countries, victimisation surveys are openly available for download. This is not only useful for substantive research (e.g. quantifying long-term crime trends), but also scrutiny over reliability and accuracy in other forms of open data, such as police recorded crime records. Both of these examples represent an interesting challenge to open data principles, since data tends to be anonymised to some degree before being made available to the public. Access to the raw records is dependent on a number of requrements (e.g. background checks, contractual agreements, ICT security measures) which might exclude many individuals due to cost and practicality.

@@

Opening up data generated by the private sector represents a significant challenge, largely due to the proprierary value to its creators [@kitchin2014data]. The aims and objectives of private companies, who have a duty to shareholders and operate in a competitive market environment, differ considerably from local and central government. That said, some datasets are released openly by private sector organisations, albiet often only a subset of what would be available as a paying customer. The website for ArcGIS, a piece of software maintained by the Environmental Systems Research Institute (ESRI), a private company, host a number of open geographic datasets on their online cloud platform (https://hub.arcgis.com/search). Indeed, many papers have made use of data collected or distributed by private organisations to explore crime and place, such as Google Street View [@langton2017residential] and Twitter [@malleson2015impact]. In this book you will learn to use the free Twitter API for such purposes in criminology (see Section 3, Topic 7).

@@

Finally, there is a specific group of open data sources that collate data collectively, generated by large groups of individuals who do not specifically belong to any organisation, but instead work together on a collaborative project. These are crowdsourced data sets. Examples include Wikipedia (https://www.wikipedia.org/), an online encyclopedia where anyone can contribute, and Flickr (https://www.flickr.com/) an online photo gallery where people can upload and tag their photos. Often, the organisations who maintain and monitor these data collection activities are charities or non-govermental organisations that do not operate for profit, but instead provide some form of social good. An example is the online reporting platform FixMyStreet (https://www.fixmystreet.com/), where people can report problems such as instances of graffiti, vandalism or environment issues. The data has been used to explore signal crimes theory, for instance, offering insight into people's experiences with incivilities [@solymosi2018crowdsourcing]. Another chapter in this book (see Section 3, Topic 6) discusses the merits and pitfalls of crowdsourced data, and what to watch out for when analysing open data of this type.

@@

Firstly, one of the biggest obstacles to collecting open data is the ability to interpret what the data means (e.g. applying a framework for its analysis), and computational skills in data scraping, wrangling and cleaning, in order to transform it into a usable format for research [@boyd2012critical]. All sorts of open data remain unanalysed, and or inaccessible, to large portions of the population, simply because they lack the skills and know-how. Although this is certainly an obstacle for data usage more generally, it represents a key challenge to the governmental bodies, in particular, on which there is an onus to ensure transparency and faciliate scrutiny. Private companies, especially those who generate open data as a by-product of their primary activity (e.g. Twitter), have little responsibility or pressure to ensure that their data is accessible and usable to the general public. Moreover, in both public and private spheres, licences and conditions on open data are not necessarily concrete, and might be subject to change with little or no notice. This is an important consideration when planning and running long-term research projects.

Secondly, despite the merits of open data in terms of remedying pitfalls in traditional survey methods, there are new threats to validity that may emerge. For instance, whilst many online resources offer an 'honest' depiction of society, uncaptured by surveys, researchers should be careful in interpreting people's communication online as completely authentic [@manovich2011trending]. This could be a result of individuals willingly managing and 'curating' their online presence, or because of wider issues such as government consorship, or cultural norms around particular topics such as sexual assault. Relatedly, researchers should be aware of issues over sampling, and ultimately the generalisability of findings that emerge from the analysis of open data. In the case of crowdsourced data, the sample is not randomly drawn from a population, but rather, it is self-selected, giving way for people willing to discuss or contribute to a particular issue, which introduced a degree of bias [@longley2012geodemographics]. Specifically, contributors tend to be men, between the ages of 20-50, with a college or university degree [@budhathoki2010participants; @haklay2010good]. Contributions to resources such as Open Street Map, which we look at in the practical exercise later, are correlated with contextual characterisics such as poverty and population density, and as such, coverage is non-uniformly distributed across urban areas [@mashhadi2013putting]. These are important to keep in mind (and be transparent about) when reporting findings based on analysis of such data.

@@

With this in mind, the following exercise utilises two different sources of open data on public transport and police recorded crime in London, England.

@@

- Accessing open data using direct downloads and Application Programming Interfaces (APIs).
- Cleaning and wrangling data for analysis.
- Visualising open spatial data.
- Comparing different sources of open data.
- Engaging with the critical questions outline above to better understand open data.

@@

In demonstrating these skills, we will be answering two key research questions. The first is a substantive empirical investigation into crime in and around London Underground stations, in the spirit of existing research into transport crime (see newton2014above). Studies in Sweden, for instance, have shown the importance of environmental and neighbourhood characteristics in determining crime concentrations at underground stations in Stockholm, along with the positioning of stations on the line [@ceccato2013security]. Investigations have also taken place into crime concentrations at bus stops in Los Angeles [@loukaitou1999hot] and the impact of intensive policing along bus corridors in Merseyside, England [@newton2004crime], amongst others. As auch, we can pose the following research question:

@@

Another way of downloading open data is through an application programming interface (API). This is a tool which defines an interface for a programme to interact with a software component or system, for example, what sort of requests or calls can be made to it, and how these can be made. Here, we are using the term 'API' to denote tools created by an open data provider to provide access to different subsets of their content. APIs facilitate scripted and programmatic extraction of content, as permitted by the API provider [@olmedilla2016harvesting]. APIs can take many different forms and be of varying quality and usefulness [@foster2016big]. For the purposes of accessing open data from the web, we are specifically talking about _RESTful_ APIs. The 'REST' stands for Representational State Transfer. These APIs work directly over the web, which means users can play with the API with relative ease in order to understand how it works [@foster2016big].

@@

```{r}
library(jsonlite) 
library(osmdata)
library(ggplot2)
library(sf)
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(patchwork)
```

@@

Reading through the TfL API documentation mentioned earlier (https://api-portal.tfl.gov.uk/docs), you will get a feel for the kind of data available. To draw conclusions about the degree to which crime occurs in and around London Underground stations, we first need spatial information so we can plot station locations on a map. In the documentation there in fact an 'API area', which offer some guidance on the types of data available, called _Stops_. We can see that this include information on bus stops by route (which are numbered e.g. 24), and underground stations by line (which are named e.g. "Bakerloo"). The example for the underground stations is a URL: https://api.tfl.gov.uk/line/bakerloo/stoppoints. This has quite an intuitive structure, since we first want to access the TfL API, look for data by line, select the name of the line we are interested in, and finally pull unformation about where stations stops. In fact, you can simply copy and paste this URL into your internet browser, and it should look something like Figure 1.

```{r tfl, out.width = "\\textwidth", fig.cap="Figure 1: example underground stations data from Transport for London", echo = F}
knitr::include_graphics("img/tfl_screenshot.png")
```

@@

This gives us an object (`api_call`) which contains all the information returned by the TfL API. JSON is slightly different to tradtional data frames with rows and columns, which we are probably quite familiar with, because the data is nested. For instance, `api_call` is classed as a data frame, but upon viewing the object using `View(api_call)` you will notice that there are lists nested within it. Another way of checking this is looping the `class()` function through all the columns in the data frame using `lapply(api_call, class)`. This demonstrates an important challenge faced by researchers when using open data, because dealing with data in this format can be messy and complicated.

@@

We can now easily visualize this data using the `ggplot2` package, which is compatable with `sf` objects.

@@

There we have it: with just a few lines of code in R, we have directly queried the Transport for London API, a public sector source of open data, and plotted a basic map of stations on the Northern underground line.

@@

```{r}
bb_sf <- getbb(place_name = "greater london united kingdom", format_out = "sf_polygon")
```

@@

```{r}
ggplot(data = bb_sf) +
  geom_sf()
```

Now we have our study region, we can scrape data from the OSM API using the `opq()` function. The function name is short for 'Overpass query', which is how users can query the Open Street Map API using search criteria. A common way of doing this is using 'Overpass turbo' (https://overpass-turbo.eu/) which allows you to query the database alongside an interactive map which automatically updates based on your results. In the interests of reproducibility consistently, we will make these queries from within R using the `osmdata` wrapper.

@@

```{r}
osm_stat_sf <- opq(bbox = bb_sf) %>%                               # select bounding box
  add_osm_feature(key = 'public_transport', value = 'station') %>% # select features
  osmdata_sf() %>%                                                 # specify class (sf or sp)
  trim_osmdata(bb_poly = bb_sf)                                    # trim by bounding box 
```

@@

```{r}
osm_stat_sf
```

@@

```{r}
osm_stat_sf <- osm_stat_sf$osm_points 
```

@@

```{r, results = F, eval = F}
osm_stat_sf %>%
  as_tibble() %>% 
  group_by(network, line) %>% 
  tally() %>% 
  View()
```

In fact, because all Northern line stations are labeled as London Underground, we only need to filter by the line.

```{r}
osm_north_sf <- osm_stat_sf %>% 
  filter(line == "Northern")
```

Niw, we can then plot these points over the station locations pulled from the TfL API. We ignore the study region boundary to get a more detailed view.

```{r}
ggplot() +
  geom_sf(data = tfl_north_sf) +
  geom_sf(data = osm_north_sf, color = "red", alpha = 0.5) 
```

As we can see, there is clearly some discrepency between the two data sources. This gives us a preliminary answer to our second research question already: data relating to London Underground stations on Open Street Map appears to be incomplete. As such, the public sector open data from TfL appears to hold some advantage over its crowdsourced alternative. But what might the impact be on studying crime in and around London Underground stations? For that, we can load in our police recorded crime data which we downloaded directly from the web earlier.

```{r}
btp_df <- read_csv("data/2020-01-btp-street.csv")
```

In its raw form, this data is a standard data frame, but we can make it spatial using some of the functions we used earlier. Note that we need to add `st_intersection()` to clip our points to our study region, because the British Transport Police are operational across the country, not just in London. To do this, we first project `bb_sf` to the British National Grid, so that we perform the intersection on data which has the same projection.

```{r}
# First, project the study region boundaries.
bb_sf <- st_transform(bb_sf, 27700)

@@

We now have the location of all crimes recorded by the British Transport Police in Greater London during January, 2020. For the purposes of this demonstration, we can define crimes occurring as 'in and around' Northern line tube stations by creating a 50 metre buffer around each station, for each source of data, and counting the number of points falling within each. It is worth noting that this definition is somewhat arbitary, and is subject to a degree of spatial inaccuracy is open police recorded crime data [see tompson2015uk].

```{r}
# Assign the same CRS.
osm_north_sf <- st_transform(osm_north_sf, 27700)
tfl_north_sf <- st_transform(tfl_north_sf, 27700)

@@

# Count number of crimes recorded within each buffer.
osm_north_sf <- osm_buff_sf %>% 
  mutate(crimes = lengths(st_intersects(osm_buff_sf, btp_sf)))

tfl_north_sf <- tfl_buff_sf %>% 
  mutate(crimes = lengths(st_intersects(tfl_buff_sf, btp_sf)))
```

@@

```{r}
p1 <- ggplot(data = osm_north_sf) +
  geom_sf(mapping = aes(colour = crimes), size = 2) +
  labs(title = "Open Street Map") +
  scale_colour_viridis_c()

@@

@@

## Conclusion

- Re-cap on what we've covered.
- Wrap-up the key points.

>>>>

Open data are a response to these shortcomings, broadening access and participation in research, removing the requirement for permissions, formal agreements and negotiations [@manovich2011trending]. Not only this, but open data can also lead to all sorts of novel insight within criminology and crime and place research, tapping into constructs and processes which are difficult to capture through surveys, interviews and other traditional measures [@solymosi2018role]. As such, it is important that social scientists, researchers, crime analysts, and others interested in making sense of the social world around them have the skills and know-how to access, accurately interpret, assess and analyse open data sets.

@@

In short, 'open data' should be data that are readily and publicly available, in a usable format, and without restrictions on usage, modification and re-distribution.

@@

As researchers studying crime and place, public sector data is particularly important. Many variables thought to explain the non-random distribution of crime, offenders and victims in space are collated and published by governmental bodies. For instance, demographic characteristics about resident populations can be collected via national censuses, with data usually released at aggregations which constitute 'neighbourhoods' - a theoretically important scale in criminology. Data describing urban structure, such as street networks, are often generated and distributed by public bodies, and can be used in street syntax analysis to assess whether the configuration of streets dictates things like violent crime victimisation [@streetsyntax2017]. In many countries, victimisation surveys are openly available for download. This is not only useful for substantive research (e.g. quantifying long-term crime trends), but also scrutiny over reliability and accuracy in other forms of open data, such as police recorded crime records. Both of these examples represent an interesting challenge to open data principles, since data tends to be anonymised to some degree before being made available to the public. Access to the raw records is dependent on a number of requirements (e.g. background checks, contractual agreements, ICT security measures) which might exclude many individuals due to cost and practicality.

@@

Opening up data generated by the private sector represents a significant challenge, largely due to the proprietary value to its creators [@kitchin2014data]. The aims and objectives of private companies, who have a duty to shareholders and operate in a competitive market environment, differ considerably from local and central government. That said, some datasets are released openly by private sector organisations, albeit often only a subset of what would be available as a paying customer. The website for ArcGIS, a piece of software maintained by the Environmental Systems Research Institute (ESRI), a private company, host a number of open geographic datasets on their online cloud platform (https://hub.arcgis.com/search). Indeed, many papers have made use of data collected or distributed by private organisations to explore crime and place, such as Google Street View [@langton2017residential] and Twitter [@malleson2015impact]. In this book you will learn to use the free Twitter API for such purposes in criminology (see Section 3, Topic 7).

@@

Finally, there is a specific group of open data sources that collate data collectively, generated by large groups of individuals who do not specifically belong to any organisation, but instead work together on a collaborative project. These are crowdsourced data sets. Examples include Wikipedia (https://www.wikipedia.org/), an online encyclopedia where anyone can contribute, and Flickr (https://www.flickr.com/) an online photo gallery where people can upload and tag their photos. Often, the organisations who maintain and monitor these data collection activities are charities or non-governmental organisations that do not operate for profit, but instead provide some form of social good. An example is the online reporting platform FixMyStreet (https://www.fixmystreet.com/), where people can report problems such as instances of graffiti, vandalism or environment issues. The data has been used to explore signal crimes theory, for instance, offering insight into people's experiences with incivilities [@solymosi2018crowdsourcing]. Another chapter in this book (see Section 3, Topic 6) discusses the merits and pitfalls of crowdsourced data, and what to watch out for when analysing open data of this type.

@@

Firstly, one of the biggest obstacles to collecting open data is the ability to interpret what the data means (e.g. applying a framework for its analysis), and computational skills in data scraping, wrangling and cleaning, in order to transform it into a usable format for research [@boyd2012critical]. All sorts of open data remain unanalyzed, and or inaccessible, to large portions of the population, simply because they lack the skills and know-how. Although this is certainly an obstacle for data usage more generally, it represents a key challenge to the governmental bodies, in particular, on which there is an onus to ensure transparency and facilitate scrutiny. Private companies, especially those who generate open data as a by-product of their primary activity (e.g. Twitter), have little responsibility or pressure to ensure that their data is accessible and usable to the general public. Moreover, in both public and private spheres, licences and conditions on open data are not necessarily concrete, and might be subject to change with little or no notice. This is an important consideration when planning and running long-term research projects.

Secondly, despite the merits of open data in terms of remedying pitfalls in traditional survey methods, there are new threats to validity that may emerge. For instance, whilst many online resources offer an 'honest' depiction of society, uncaptured by surveys, researchers should be careful in interpreting people's communication online as completely authentic [@manovich2011trending]. This could be a result of individuals willingly managing and 'curating' their online presence, or because of wider issues such as government censorship, or cultural norms around particular topics such as sexual assault. Relatedly, researchers should be aware of issues over sampling, and ultimately the generalizability of findings that emerge from the analysis of open data. In the case of crowdsourced data, the sample is not randomly drawn from a population, but rather, it is self-selected, giving way for people willing to discuss or contribute to a particular issue, which introduced a degree of bias [@longley2012geodemographics]. Specifically, contributors tend to be men, between the ages of 20-50, with a college or university degree [@budhathoki2010participants; @haklay2010good]. Contributions to resources such as Open Street Map, which we look at in the practical exercise later, are correlated with contextual characteristics such as poverty and population density, and as such, coverage is non-uniformly distributed across urban areas [@mashhadi2013putting]. These are important to keep in mind (and be transparent about) when reporting findings based on analysis of such data.

@@

With this in mind, the following exercise utilizes two different sources of open data on public transport and police recorded crime in London, England.

@@

- Accessing open data using direct downloads and Application Programming Interfaces (APIs).
- Cleaning and wrangling data for analysis.
- Visualizing open spatial data.
- Comparing different sources of open data.
- Engaging with the critical questions outline above to better understand open data.

@@

In demonstrating these skills, we will be answering two key research questions. The first is a substantive empirical investigation into crime in and around London Underground stations, in the spirit of existing research into transport crime (see newton2014above). Studies in Sweden, for instance, have shown the importance of environmental and neighbourhood characteristics in determining crime concentrations at underground stations in Stockholm, along with the positioning of stations on the line [@ceccato2013security]. Investigations have also taken place into crime concentrations at bus stops in Los Angeles [@loukaitou1999hot] and the impact of intensive policing along bus corridors in Merseyside, England [@newton2004crime], amongst others. As such, we can pose the following research question:

@@

Another way of downloading open data is through an application programming interface (API). This is a tool which defines an interface for a program to interact with a software component or system, for example, what sort of requests or calls can be made to it, and how these can be made. Here, we are using the term 'API' to denote tools created by an open data provider to provide access to different subsets of their content. APIs facilitate scripted and programmatic extraction of content, as permitted by the API provider [@olmedilla2016harvesting]. APIs can take many different forms and be of varying quality and usefulness [@foster2016big]. For the purposes of accessing open data from the web, we are specifically talking about _RESTful_ APIs. The 'REST' stands for Representational State Transfer. These APIs work directly over the web, which means users can play with the API with relative ease in order to understand how it works [@foster2016big].

@@

```{r packages}
library(jsonlite) 
library(osmdata)
library(ggplot2)
library(sf)
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(patchwork)
```

@@

Reading through the TfL API documentation mentioned earlier (https://api-portal.tfl.gov.uk/docs), you will get a feel for the kind of data available. To draw conclusions about the degree to which crime occurs in and around London Underground stations, we first need spatial information so we can plot station locations on a map. In the documentation there in fact an 'API area', which offer some guidance on the types of data available, called _Stops_. We can see that this include information on bus stops by route (which are numbered e.g. 24), and underground stations by line (which are named e.g. "Bakerloo"). The example for the underground stations is a URL: https://api.tfl.gov.uk/line/bakerloo/stoppoints. This has quite an intuitive structure, since we first want to access the TfL API, look for data by line, select the name of the line we are interested in, and finally pull information about where stations stops. In fact, you can simply copy and paste this URL into your internet browser, and it should look something like Figure 1.

```{r tfl, out.width = "\\textwidth", fig.cap="example of data from Transport for London", echo = F}
knitr::include_graphics("img/tfl_screenshot.png")
```

@@

This gives us an object (`api_call`) which contains all the information returned by the TfL API. JSON is slightly different to traditional data frames with rows and columns, which we are probably quite familiar with, because the data is nested. For instance, `api_call` is classed as a data frame, but upon viewing the object using `View(api_call)` you will notice that there are lists nested within it. Another way of checking this is looping the `class()` function through all the columns in the data frame using `lapply(api_call, class)`. This demonstrates an important challenge faced by researchers when using open data, because dealing with data in this format can be messy and complicated.

@@

We can now easily visualize this data using the `ggplot2` package, which is compatible with `sf` objects.

@@

There we have it: with just a few lines of code in R, we have queried the Transport for London API, a public sector source of open data, and plotted a basic map of stations on the Northern underground line.

@@

```{r bb}
bb_sf <- getbb(place_name = "greater london united kingdom", format_out = "sf_polygon")
```

@@

```{r bbmap}
ggplot(data = bb_sf) +
  geom_sf()
```

Now we have our study region, we can scrape data from the OSM API using the `opq()` function. The function name is short for 'Overpass query', which is how users can query the Open Street Map API using search criteria. A common way of doing this is using 'Overpass turbo' (https://overpass-turbo.eu/) which allows you to query the database alongside an interactive map which automatically updates based on your results. In the interests of consistency, we will make these queries from within R using the `osmdata` wrapper.

@@

```{r opq}
osm_stat_sf <- opq(bbox = bb_sf) %>%                               # select bounding box
  add_osm_feature(key = 'public_transport', value = 'station') %>% # select features
  osmdata_sf() %>%                                                 # specify class
  trim_osmdata(bb_poly = bb_sf)                                    # trim by bounding box 
```

@@

```{r printstations}
osm_stat_sf
```

@@

```{r stationpoints}
osm_stat_sf <- osm_stat_sf$osm_points 
```

@@

```{r freqtab, results = F, eval = F}
osm_stat_sf %>%
  as_tibble() %>% 
  group_by(network, line) %>% 
  tally() %>% 
  View()
```

In fact, because all Northern line stations are labeled as "London Underground", we only need to filter by the line.

```{r filterline}
osm_north_sf <- osm_stat_sf %>% 
  filter(line == "Northern")
```

Now, we can then plot these points over the station locations pulled from the TfL API. We do not plot the study region boundary in order to get a more detailed, local view.

```{r mapline}
ggplot() +
  geom_sf(data = tfl_north_sf) +
  geom_sf(data = osm_north_sf, color = "red", alpha = 0.5) 
```

As we can see, there is clearly some discrepancy between the two data sources. There are slight differences in the exact point locations of stations, but more saliently,  Open Street Map appears to be missing stations, especially in Central and South London. This could be due to a number of reasons, amongst them, variation in residents' willingness to contribute to information about their local area, and the demographic characteristics known to influence the volume of contributions [@mashhadi2013putting]. Given that South London is historically less wealthy in comparison to the North, for instance, this would certainly be an interesting avenue to pursue. Interestingly, these missing stations _have_ actually been recorded by contributors in Open Street Map, but _without_ information about the line on which the station is located. We can see this by plotting out all Open Street Map stations using `osm_stat_sf`. That said, without local knowledge, an alternative open data source, or a critical approach to using open data, well-intentioned researchers might draw erroneous conclusions from filtering stations tagged as on the Northern line. This gives us a preliminary answer to our second research question already: the public sector open data from TfL appears to hold some advantage over its crowdsourced alternative, Open Street Map, in terms of London Underground lines.

But, what might the impact of this be on studying crime in and around London Underground stations, given the differences observed between the two open data sources? For that, we can load in our British Transport Police data which we downloaded directly from the web earlier.

```{r crimeload}
btp_df <- read_csv("data/2020-01-btp-street.csv")
```

In its raw form, this data is a standard data frame, but we can make it spatial using some of the functions we used earlier. Note that we need to add `st_intersection()` to clip our points to our study region, because the British Transport Police are operational across the country, not just in London. To do this, we first project `bb_sf` to the British National Grid, so that we perform the intersection on data which have the same projection.

```{r crimespatial}
# First, project the study region boundaries.
bb_sf <- st_transform(bb_sf, 27700)

@@

We now have the location of all crimes recorded by the British Transport Police in Greater London during January, 2020. For the purposes of this demonstration, we can define crimes occurring as 'in and around' Northern line tube stations by creating a 50 meter buffer around each station, for each source of data, and counting the number of points falling within each. It is worth noting that this definition is somewhat arbitrary, and is subject to a degree of spatial inaccuracy is open police recorded crime data [see tompson2015uk], but serves to facilitate this demonstration.

```{r buffer}
# Assign the same CRS.
osm_north_sf <- st_transform(osm_north_sf, 27700)
tfl_north_sf <- st_transform(tfl_north_sf, 27700)

@@

# Count number of crimes recorded within each buffer.
osm_north_sf <- osm_buff_sf %>% 
  mutate(crimes = lengths(st_intersects(osm_buff_sf, btp_sf)))
tfl_north_sf <- tfl_buff_sf %>% 
  mutate(crimes = lengths(st_intersects(tfl_buff_sf, btp_sf)))
```

@@

```{r crimemapcompare}
p1 <- ggplot(data = osm_north_sf) +
  geom_sf(mapping = aes(colour = crimes), size = 2) +
  labs(title = "Open Street Map") +
  scale_colour_viridis_c()

@@

A number of factors emerge from this visualization. First, issues arising disparity between the stations identified on the Northern line are compounded. Using the Open Street Map data in isolation, we are grossly underestimating the the number of crimes occurring in and around Northern line stations. This could have significant implications for how police allocate resource across the underground network. Secondly, the spatial patterning of crime on underground stations differs considerably between the two data sources. Using the Open Street Map data, the final station on the line, Morden, has the greatest concentration of crimes, whereas the TfL data suggests this is in the city centre, at Tottenham Court Road. The conclusions drawn are starkly different, and would determine the consistency of findings with existing research examining crime at underground stations [@ceccato2013security].

That said, this is not to say that Open Street Map is an inadequate source of open data for crime and place research. Firstly, it is an ever-growing resource. It is plausible (indeed, likely) that in the near future, the missing information about London Underground lines will be completed. Secondly, as noted, systematic variation in the extent to which individuals have contributed to the database can generate interesting discussions and avenues of research in its own right. Thirdly, this is simply one of thousands of features contained in the Open Street Map database. If we were interested in examining concentrations of bicycle theft from bike rental docking stations (so-called "Boris bikes") in Greater London, we could query open data APIs from TfL and Open Street Map, just as we did earlier, but using slightly amended criteria. This is demonstrated below, all in one code chunk.

```{r bikexample}
bb_sf <- getbb(place_name = "greater london", format_out = "sf_polygon")

osm_bike_sf <- opq(bbox = bb_sf) %>%                                 
  add_osm_feature(key = 'amenity', value = 'bicycle_rental') %>%     
  osmdata_sf() %>%                                                  
  trim_osmdata(bb_poly = bb_sf)

osm_bike_sf <- osm_bike_sf$osm_points

osm_bike_sf <- osm_bike_sf %>% 
  filter(brand == "Santander Cycles")

tfl_bike_sf <- fromJSON(readLines("https://api.tfl.gov.uk/bikepoint"))

tfl_bike_sf <- tfl_bike_sf %>%
  st_as_sf(coords = c(x = "lon", y = "lat"), crs = 4326)

ggplot() + 
  geom_sf(data = osm_bike_sf) +
  geom_sf(data = tfl_bike_sf, col = "red", alpha = 0.4)
```

As showcased, the resulting visualizations are highly similar (a Spatial Point Pattern Test will confirm this, see Section 4 Topic 4). Refer back to the example earlier if some of the code is unclear. Note that this is a fantastic benefit of using an API wrapper from within R, because the code used to query each open data source can easily be re-used, with minor amendments, to extract different features.

# Discussion

## Summary

This chapter has sought to introduce open data as a novel, growing and invaluable tool in crime and place research through a review of key fundamentals and a substantive demonstration within R. We have defined open data, and outlined some key types of open information available, along with their respective strengths and weaknesses. An important component of this review has been encourage an engaged and critical research approach to using open data. Open data is both a rich resource of dependent and independent variables for researching the geography of crime, and an interesting research topic in and of itself as a tool for providing insight overlooked by traditional data sources. By way of an example, we accessed different sources of open data in order to explore crime concentrations at London Underground stations: police recorded crime data via a direct download from a public sector website, transport data via directly querying a public sector API, hosted by Transport for London, and the equivalent transport data retrieved from a crowdsourced database, Open Street Map, using an API wrapper. We found key differences between the two sources of transport data. Specifically, missing information in Open Street Map resulted in a skewed picture of crime occurring in and around underground stations. This highlighted both the power of open data, but also its shortcomings. We concluded with an additional demonstration using bike rental docking stations in Greater London, which showcased a scenario in which both public sector and crowdsourced open data provide unique (and comparable) insight.

@@
